---
title: "Assignment"
author: "Jungsok Lee"
date: "2019년 2월 28일"
output: html_document
---

# 1. Code for reading in the dataset and/or processing the data
## Loading and preprocessing the data
firstly, I read data form activity.csv file which is placed at current working directory, then assigned the data to variable dat.

Then, I sum everyday total steps with tapply function, made dataframe having dates and total steps at that day as columns, and then removed rows that contains NA at steps column.
```{r readandproc, result = "hide"}
dat <- read.csv("activity.csv")
View(dat)
class(dat$date)
dat$date <- as.Date(as.character(dat$date), "%Y-%m-%d")

steps_by_dates <- tapply(dat$steps, dat$date, sum)
steps_by_dates <- data.frame(names(steps_by_dates), steps_by_dates,row.names = 1:length(steps_by_dates))
names(steps_by_dates) <- c("dates", "steps")
steps_by_dates$dates <- as.Date(as.character(steps_by_dates$dates), "%Y-%m-%d")
steps_by_dates$steps <- as.numeric(as.character(steps_by_dates$steps))
steps_by_dates_T <- steps_by_dates[!is.na(steps_by_dates$steps),]


```

# 2. Histogram of the total number of steps taken each day

I made a histogram using dataframe I made right before.
```{r histogram1}
hist(steps_by_dates_T$steps, xlab = "Total Steps", col = "blue", main = "Histogram of Total Steps")
```


# 3. Mean and median number of steps taken each day

I calcuated Mean and median Steps taken at each day.
```{r meanmedian}
sprintf("Mean : %.2f", mean(steps_by_dates_T$steps))
sprintf("Median : %d", median(steps_by_dates_T$steps))
```


# 4. Time series plot of the average number of steps taken

I plotted type series plot of the average number of steps taken.
```{r timeseriplot}
plot(steps_by_dates_T$dates, steps_by_dates_T$steps, xlab = "Dates", ylab = "Steps", type = "l", col = "red")
```


# 5. The 5-minute interval that, on average, contains the maximum number of steps

I take the 5-minute time interval that contains the maximun number of steps
```{r maxsteps}
steps_by_interval <- tapply(dat$steps, dat$interval, mean, na.rm = TRUE)
names(steps_by_interval[steps_by_interval == max(steps_by_interval)])
```

# 6. Code to describe and show a strategy for imputing missing data
## Imputing missing values
I replace NA value using mean value.

```{r impute}
dat[is.na(dat$steps), 1] <- mean(dat$steps, na.rm = T)
```


# 7. Histogram of the total number of steps taken each day after missing values are imputed

I made histogram using imputed data.
```{r hist-rep}
steps_by_dates <- tapply(dat$steps, dat$date, sum)
steps_by_dates <- data.frame(names(steps_by_dates), steps_by_dates,row.names = 1:length(steps_by_dates))
names(steps_by_dates) <- c("dates", "steps")
steps_by_dates$dates <- as.Date(as.character(steps_by_dates$dates), "%Y-%m-%d")
steps_by_dates$steps <- as.numeric(as.character(steps_by_dates$steps))
hist(steps_by_dates$steps, xlab = "Total Steps", col = "red", main = "Histogram of Total Steps")
```



# 8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

I plotted panel plot comparing the average number of steps taken per 5-minute interval across weekdays.

I used dplyr to group the data by weekdays.

```{r panelplot}
Sys.setlocale("LC_TIME", "English")
library(dplyr)
library(lattice)
dat$days <- weekdays(dat$date)

week <- subset(dat, days %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))
week <- tbl_df(week)
week$interval <- as.factor(week$interval)
week <- group_by(week, interval)
week_steps <- summarize(week, mean(steps))
week_steps$interval <- as.numeric(as.character(week_steps$interval))
week_steps$day <- "weekday"

weekend <- subset(dat, days %in% c("Saturday", "Sunday"))
weekend <- tbl_df(weekend)
weekend$interval <- as.factor(weekend$interval)
weekend <- group_by(weekend, interval)
weekend_steps <- summarize(weekend, mean(steps))
weekend_steps$interval <- as.numeric(as.character(weekend_steps$interval))
weekend_steps$day <- "weekend"

steps_mean<-rbind(week_steps, weekend_steps)
names(steps_mean)[2] <- "steps"
with(steps_mean, xyplot(steps ~ interval|day, type = "l", layout = c(1,2), ylab = "Number of Steps"))
```






## What is mean total number of steps taken per day?
### 10766.19 steps


## What is the average daily activity pattern?
### people usually take most of their daily steps during morning.



## Are there differences in activity patterns between weekdays and weekends?
### Compared to weekdays, In weekend step distributions are relatively even during daytime. It doesn't have a morning spike.

